---
title: "PA1_template"
author: "Aleksandr Kliushev"
date: "14.06.2015"
output: html_document
---
This research  about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up.

Load library
```{r}
library(dplyr)
library(ggplot2)
```

1. The first step of research is a load, read and transform (to "tbl" format) data
```{r}
setwd("C:\\Users\\123\\Documents\\R\\coursera\\Reproduce Research\\PA1")
act_data<-tbl_df(read.csv("activity.csv"))
```
Let's see data
```{r}
act_data
```
Group data for days
```{r}
act_day<-act_data%>%
      group_by(date)%>%
      summarise(step_sum=sum(steps,na.rm = T))
act_day$date<-as.POSIXct(act_day$date)
act_day
```

2. Mean and median number of steps
2.a Plot a histogram number of steps
```{r}
hist(act_day$step_sum,breaks = 15,
      main = "Histogram steps per day",xlab = "Steps count")  
```  

2.b Count mean and median 
```{r}
step_mean<-mean(act_day$step_sum)
stem_med<-median(act_day$step_sum)
```  
The mean of step in day is `r format(step_mean)` and  
median is `r stem_med`

3. Plot daily activity
```{r}
g<-ggplot(data = act_data,aes(interval,steps))
g+geom_line()
```
How we can see the 600 - 2000 interval is contains the maximum number of steps.

4.Imputing missing values
4.a Count the missing values
```{r}
mis_v<-count(act_data[is.na(act_data$steps),1])[[1]]
```
Count the missing values is `r mis_v`

4.b Create new df, where missing value equal mean of 5 second interval
```{r}
act_int<-act_data%>%
      group_by(interval)%>%
      summarise(step_mean=mean(steps,na.rm = T))
act_data_no_m<-(left_join(x=act_data,y = act_int,by =c("interval"="interval"))%>%
      mutate(step_all = ifelse(is.na(steps),step_mean,steps)))[,
                                                 c("date","interval","step_all")]
```
4.c Create hist without missing value
```{r}
act_day_no_m<-act_data_no_m%>%
      group_by(date)%>%
      summarise(step_sum=sum(step_all,na.rm = T))
act_day_no_m$date<-as.POSIXct(act_day_no_m$date)
hist(act_day_no_m$step_sum,breaks = 15,
      main = "Histogram steps per day without NA",xlab = "Steps count")
```

4.d Count mean and median without NA
```{r}
step_mean_1<-mean(act_day_no_m$step_sum)
stem_med_1<-median(act_day_no_m$step_sum)
```  
The mean of step in day is `r format(step_mean_1)` and  
median is `r format(stem_med_1)`

5.Differences in activity patterns between weekdays and weekends
5.a Make a column with weekday/weekends values
```{r}
act_data_no_m$weekday<-
      factor(weekdays(as.POSIXct(act_data_no_m$date),abbreviate = T),
                levels = c("Ïí","Âò","Ñð","×ò","Ïò","Ñá","Âñ"),ordered=TRUE) 
act_data_no_m$weekday_l<-ifelse(act_data_no_m$weekday=="Ïí"
                                | act_data_no_m$weekday=="Âò"
                                | act_data_no_m$weekday=="Ñð"
                                | act_data_no_m$weekday=="×ò"
                                | act_data_no_m$weekday=="Ïò"
                                ,"Weekdays","Weekends")
```
5.b Make a df, group by interval an weekdays_l
```{r}
act_int_no_m<-act_data_no_m%>%
      group_by(interval,weekday_l)%>%
      summarise(step_mean=mean(step_all))
```
5.c Make a graf
```{r}
g<-ggplot(data = act_int_no_m,aes(interval,step_mean))
g+geom_line()+facet_grid(. ~ weekday_l)
```


